#### Exercise 2: Edgar Anderson's Iris Data

In this exercise, you will analyze a well-known `iris` dataset, which you studied in Machine Learning In Business Analytics course. The dataset contains measurements in centimeters of the variables sepal length and width and petal length and width, respectively for each type of iris, namely, setosa, versicolor, and virginica.

__2.a__ Load the dataset `iris` and convert it into `tibble`. How many columns does the dataset have? Name data types of these columns.

```{r, message=FALSE}

data(iris)

tibble.iris <- as_tibble(iris)

#number of columns
ncol(tibble.iris)

#datatype of columns

class(tibble.iris$Sepal.Length)
class(tibble.iris$Sepal.Width)
class(tibble.iris$Petal.Length)
class(tibble.iris$Petal.Width)
class(tibble.iris$Species)







```

__2.b__ Print out only species and its length of a sepal in ascending order. Print out same columns in using descending order of sepal length.

```{r, message = FALSE}

tibble.iris %>% 
  arrange(desc(Sepal.Length)) %>% 
  select(Sepal.Length, Species)

tibble.iris %>% 
  arrange(Sepal.Length) %>% 
  select(Sepal.Length, Species)

```

__2.c__ Create a new object `iris_species` and assign to it the `iris` tibble grouped by the type of `Species`. How many entries does each `Species` have?

```{r, message=FALSE}


iris_species <- tibble.iris %>% 
  group_by(Species)

Numberofentriesbyspecies <- iris_species %>%   
  summarise(Species_entries = n())

print(Numberofentriesbyspecies)




```

__2.d__ Print out the average sepal's and petal's length and width for each species. What can be noticed?

```{r, message=FALSE}

tibble.iris %>%
  group_by(Species) %>%
  summarize(Sepal.Length.mean = mean(Sepal.Length), Petal.Length.mean = mean(Petal.Length), Sepal.Width.mean = mean(Sepal.Width), Petal.Width.mean = mean(Petal.Width))





```

__2.e__ Modify `iris_species` by adding a new column of standardized petal's length (i.e., you need to subtract a mean value from each observation and divide by standard deviation). Print the maximum values of this new variable for each species.

```{r, message=FALSE}

### your code goes here

```

__2.f__ Using the original `iris` tibble visualize the relation between petal's length and petal's width by plotting a scatter chart. Bonus: display a (linear) regression line without confidence intervals.

```{r, message = FALSE}

### your code goes here

```

__2.g__ Modify previous plot by using different colors for each species only for the scatter chart and not for the regression line.

```{r, message = FALSE}

### your code goes here

```
