#### Exercise 2: Edgar Anderson's Iris Data

In this exercise, you will analyze a well-known `iris` dataset, which you studied in Machine Learning In Business Analytics course. The dataset contains measurements in centimeters of the variables sepal length and width and petal length and width, respectively for each type of iris, namely, setosa, versicolor, and virginica.

__2.a__ Load the dataset `iris` and convert it into `tibble`. How many columns does the dataset have? Name data types of these columns.

```{r, message=FALSE}

data(iris)

tibble.iris <- as_tibble(iris)

#number of columns

kable(ncol(tibble.iris), col.names = "Number of columns in the iris Data set",
      align= 'l')

#class of columns

column_class<- tibble.iris %>% 
    summarise_all(class) %>% 
    gather(variable, class)

kable(column_class)


```

__2.b__ Print out only species and its length of a sepal in ascending order. Print out same columns in using descending order of sepal length.

```{r, message = FALSE}

S_L_Descending<-tibble.iris %>% 
  arrange(desc(Sepal.Length)) %>% 
  select(Sepal.Length, Species)

kable(head(S_L_Descending), align= 'l')



S_L_Ascending <- tibble.iris %>% 
  arrange(Sepal.Length) %>% 
  select(Sepal.Length, Species)

kable(head(S_L_Ascending), align= 'l')

```

__2.c__ Create a new object `iris_species` and assign to it the `iris` tibble grouped by the type of `Species`. How many entries does each `Species` have?

```{r, message=FALSE}


iris_species <- tibble.iris %>% 
  group_by(Species)

Numberofentriesbyspecies <- iris_species %>%   
  summarise(Species_entries = n())

kable(Numberofentriesbyspecies)




```

__2.d__ Print out the average sepal's and petal's length and width for each species. What can be noticed?

```{r, message=FALSE}

Average <- tibble.iris %>%
  group_by(Species) %>%
  summarize(Sepal.Length.mean = mean(Sepal.Length), Petal.Length.mean = mean(Petal.Length), Sepal.Width.mean = mean(Sepal.Width), Petal.Width.mean = mean(Petal.Width))

kable(Average)




```

__2.e__ Modify `iris_species` by adding a new column of standardized petal's length (i.e., you need to subtract a mean value from each observation and divide by standard deviation). Print the maximum values of this new variable for each species.

```{r, message=FALSE}

#Not clear if we have to standardize by species or on the whole data set. we will do it by species becuase it's asked to use iries_species

std_petal.lenght<-iris_species %>% mutate(STD_Petal.Lenght = (Petal.Length-mean(Petal.Length))/sd(Petal.Length)) %>%
  summarise(max = max(STD_Petal.Lenght))

kable(std_petal.lenght)



```

__2.f__ Using the original `iris` tibble visualize the relation between petal's length and petal's width by plotting a scatter chart. Bonus: display a (linear) regression line without confidence intervals.

```{r, message = FALSE}


ggplot(data=tibble.iris, aes(x=Petal.Length , y=Petal.Width)) +
  stat_smooth(method = "lm", se = FALSE) +
  geom_point(size=2, color="#690000") +
  ggtitle("Petal.Length vs Petal.Width") +
  labs(x="Petal.Length" , y="Petal.Width") 
  


```

__2.g__ Modify previous plot by using different colors for each species only for the scatter chart and not for the regression line.

```{r, message = FALSE}

ggplot(data=tibble.iris, aes(x=Petal.Length , y=Petal.Width, color = Species)) +
  geom_point(size=2) +
  ggtitle("Petal.Length vs Petal.Width") +
  labs(x="Petal.Length" , y="Petal.Width")+
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE , color="black")




```
